Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-29 prob.tex
prob.tex \subsection{Classical Interval-valued probability measures} Start typing the meaning of convex...

\begin{lemma}\label{lem:classicalProbabilityMeasure}Given a sample
space~$\Omega$ and its event~$\events$, a function~$\bar{\mu}:\events\rightarrow[0,1]$
is a classical interval-valued probability measure if and only if
$\bar{\mu}$ satisfies the following conditions: 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$.
\item $\bar{\mu}(\Omega)=[1,1]$. 
\item For any event $E$, $\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)$.
\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\bar{\mu}\left(E_{i}\right)$,
where $\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}r_{i}\right]$.
We may drop the preposing $\mathscr{I}$ when summands are clearly
intervals. 
\end{itemize}
\qed\end{lemma}

@@

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex}, \emph{2-monotone}, or\emph{
supermodular} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.
\end{itemize}
\qed\end{definition}

>>>>

\begin{lemma}\label{lem:classicalProbabilityMeasure}Given a sample
space~$\Omega$ and its event~$\events$, a function~$\bar{\mu}:\events\rightarrow[0,1]$
is a classical interval-valued probability measure if and only if
$\bar{\mu}$ satisfies the following conditions: 
\begin{itemize}
\item $\bar{\mu}(\emptyset)=[0,0]$.
\item $\bar{\mu}(\Omega)=[1,1]$. 
\item For any event $E$, 
\begin{equation}
\bar{\mu}\left(\Omega\backslash E\right)=\left[1,1\right]\tensor*[_{\mathscr{I}}]{-}{}\bar{\mu}\left(E\right)\textrm{ .}\label{eq:ClassicalInterval-valuedProbability-Complement}
\end{equation}
\item For a collection $\left\{ E_{i}\right\} _{i=1}^{N}$ of pairwise disjoint
events, we have $\bar{\mu}\left(\bigcup_{i=1}^{N}E_{i}\right)\subseteq\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}\bar{\mu}\left(E_{i}\right)$,
where $\tensor*[_{\mathscr{I}}]{\sum}{_{i=1}^{N}}[l_{i},r_{i}]=\left[\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}l_{i},\tensor*[_{\mathbb{R}}]{\sum}{_{i=1}^{N}}r_{i}\right]$.
We may drop the preposing $\mathscr{I}$ when summands are clearly
intervals. 
\end{itemize}
\qed\end{lemma}

@@

\begin{definition}~Given an interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$:
\begin{itemize}
\item A \emph{core}\footnote{The core is also called a structure~\cite{Weichselberger2000}.}
of $\bar{\mu}$ is the set $\mathrm{core}\left(\bar{\mu}\right)=\left\{ \textrm{probability measure }\pmeas:\events\rightarrow[0,1]\middle|\forall E\in\events.\pmeas\left(E\right)\in\bar{\mu}\left(E\right)\right\} $
\cite{GilboaSchmeidler1994,Marinacci1999,Teran2014}.
\item $\bar{\mu}$ is called \emph{convex}, \emph{2-monotone}, or\emph{
supermodular} if $\bar{\mu}\left(E_{1}\cup E_{2}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{1}\cap E_{2}\right)\subseteq\bar{\mu}\left(E_{1}\right)\tensor*[_{\mathscr{I}}]{+}{}\bar{\mu}\left(E_{2}\right)$
for all $E_{1},E_{2}\in\events$~\cite{Shapley1965,GilboaSchmeidler1994,Marinacci1999,Teran2014,Grabisch2016}.\footnote{\yutsung{In order to simplify the discussion, let $l$ be the left-end
of an interval-valued probability measure~$\bar{\mu}$. Because of
equation~(\ref{eq:ClassicalInterval-valuedProbability-Complement}),
$\bar{\mu}$ is convex if and only if 
\begin{equation}
l\left(E_{1}\cup E_{2}\right)+l\left(E_{1}\cap E_{2}\right)\ge l\left(E_{1}\right)+l\left(E_{2}\right)\textrm{ ,}\label{eq:convex-game}
\end{equation}
which is a special case of the Dempster-Shafer condition
\begin{equation}
l\left(\bigcup_{i=1}^{N}E_{i}\right)\ge\sum_{I\subseteq\left\{ 1,\ldots,N\right\} }\left(-1\right)^{\left|I\right|+1}l\left(\bigcap_{i\in I}E_{i}\right)\textrm{ .}\label{eq:Dempster-Shafer-game}
\end{equation}
Therefore, in order to understand the meaning of equation~(\ref{eq:convex-game}),
we could try to understand meaning of the Dempster-Shafer belief function.
Unfortunately, when people introduce the Dempster-Shafer theory, they
usually don't start from equation~(\ref{eq:Dempster-Shafer-game}).
Instead, they introduce a basic belief assignment~$m\left(E\right)=\sum_{E'\subseteq E}\left(-1\right)^{\left|E\setminus E'\right|}l\left(E'\right)$
first, and $m\left(E\right)$ expresses the proportion of all relevant
and available evidence that supports the claim that the actual state
belongs to $A$ but to no particular subset of $A$. Then, equation~(\ref{eq:Dempster-Shafer-game})
is equivalent to $m\left(E\right)\ge0$ for all $E$~\cite{Grabisch2016},
and the later statement is intuitive.}}
\end{itemize}
\qed\end{definition}
